### 2009-11-27 doc/tech_doc/client/client_technical.tex
fixing the broker section

All capabilities are enabled for three different grid flavours
(Production ARC, ARC1 and gLite~\cite{glite}) through a modular design
using plugins specialized for each supported middleware. Future
extensions to support additional middlewares involve plugin
compilation only i.e., no recompilation of main libraries or clients
is necessary.

Using the library, a set of command line tools have been built which
puts the library's functionality at the fingertips of users. While
this documentation will illustrate how such command line tools can be
built, the main documentation of the command line tools is given in
the client user manual~\cite{ui}.

In the following we will give a functionality overview in
Section~\ref{sec:FuncOver} while all technical details will be given
in Section~\ref{sec:Implementation}. Section~\ref{sec:cli} will
show through examples how command line interfaces can be built upon
the library.

@@

The new {\libarcclient} makes extensive use of plugins for command
handling. These plugins are handled by a set of higher level classes
which thus are the ones to offer the plugin functionality to external
calls. In this section an overview of the library's main functionality
is given which also introduces the most important higher level
classes.

@@

\section{Job Management}

Once a job is submitted, job related information (job identification
string, cluster etc.) is stored in a local XML file which stores this 
information for all active jobs. This file may contain jobs running on
completely different grid flavours, and thus job management should be
handled using plugins similar to resource discovery and job
submission. The job managing plugin is called the {\JobController} and
it is supported by the {\JobSupervisor} and {\Job} classes.

@@

\chapter{The ARC Brokering Module}
\label{sec:brokering}

The {\Broker} inherits from the {\ACC} base class in order to be
loadable by the ARC \texttt{Loader}. It is the base class of the
specialized {\Broker} and it implements the method for reducing a list
of resources found by resource discovery (the list of
{\ExecutionTarget}s residing within the {\TargetGenerator}) to a list
of resources capable of running a certain job:

@@

The {\Benchmark} ranks the {\ExecutionTarget}s according to their CPU performance. The most 
reliable comparison is achieved through the usage of a benchmark scenario, and the {\Benchmark}
uses the CINT2000 (Integer Component of SPEC CPU2000)\footnote{http://www.spec.org/cpu2000/CINT2000/} 
benchmark for this purpose.

The {\texttt SortTargets} method has two steps:

\begin{enumerate}
\item{{\ExecutionTarget}s not publishing the specint2000 benchmark information are removed from the list 
  of possible targets as their performance is unknown.}
\item{The {\ExecutionTarget}s are ranked such that the {\ExecutionTarget} with highest specint2000 value 
  receives top ranking}
\end{enumerate}

@@

The {\texttt SortTargets} method has three steps:

\begin{enumerate}
\item{{\ExecutionTarget}s not publishing WaitingJobs, TotalSlots and FreeSlots are removed from the list of possible targets 
as it is impossible to determine their queue length and perform load balancing.}
\item{The {\ExecutionTarget}s are ranked according to their queue length relative to the number of slots/CPUs. Zero queue 
{\ExecutionTarget}s is ranked first.}
\item{If more than one {\ExecutionTarget} has zero queue, the targets are randomly reshuffled based upon how many free slots 
they have, e.g. if two {\ExecutionTarget}s have zero queue and they have 90 and 10 free slots respectively, then the first
{\ExecutionTarget} has a 90\% probability of becoming the top ranked cluster.}
\end{enumerate}

@@

\bibliography{grid}

>>>>

All capabilities are enabled for three different grid flavours
(Production ARC, Web Service ARC and gLite~\cite{glite}) through a
modular design using plugins specialized for each supported
middleware. Future extensions to support additional middlewares
involve plugin compilation only i.e., no recompilation of main
libraries or clients is necessary.

Using the library, a set of command line tools have been built which
puts the library's functionality at the fingertips of users. This
documentation is not intended to document the developed CLI but the
concept of how to build command line tools will be
demonstrated. Readers interested in the user interface are recommended
to read the client user manual~\cite{ui}.

@@

The new {\libarcclient} makes extensive use of plugins for command
handling. These plugins are handled by a set of higher level classes
which thus are the ones to offer the plugin functionality to external
calls. In this section an overview of the library's main functionality
is given which also introduces the most important higher level
classes. Readers interested in the library API are recommended to look
up the online API documentation~\cite{libarcclientAPI}.

@@

\section{Job Management}
Once a job is submitted, job related information (job identification
string, cluster etc.) is stored in a local XML file which stores this 
information for all active jobs. This file may contain jobs running on
completely different grid flavours, and thus job management should be
handled using plugins similar to resource discovery and job
submission. The job managing plugin is called the {\JobController} and
it is supported by the {\JobSupervisor} and {\Job} classes.

@@

\chapter{The ARC Brokering Module}
\label{sec:brokering}
The ARC brokering module is made up of two kinds of classes: one
brokering base class and specialized classes derived thereof. The
brokering base class which implements the method for reducing a list
of resources found by resource discovery (the list of
{\ExecutionTarget}s residing within the {\TargetGenerator}) to a list
of resources capable of running a certain job:

@@

The {\Benchmark} ranks the {\ExecutionTarget}s according to their
benchmark performance. Through the command line tool (see the user
manual\cite{ui} for reference) this specialized broker takes a user
specified benchmark as input and ranks the {\ExecutionTarget}s
according to their published benchmark performance. If no benchmark is
specified the CINT2000 (Integer Component of SPEC
CPU2000)\footnote{http://www.spec.org/cpu2000/CINT2000/} benchmark is
used as default.

@@

@@

\bibliography{grid, libarcclient}
